Disturbance Assimilation

### 2021-06-10 Paper.Rmd
spent the morning working on the Methods section
model output for EnKF figure; config to render paper to PDF

---
title: "Disturbance Assimilation"
author: "Michael Dietze"
date: '`r Sys.Date()`'
output:
  html_document: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    keep_tex: true
bibliography: bibliography.bibtex
---

@@

# Outline

# Abstract

>>>>

---
title: "Disturbance Assimilation"
author: "Michael Dietze"
date: '`r Sys.Date()`'
output:
  pdf_document: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    keep_tex: true
  html_document: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    keep_tex: true
bibliography: bibliography.bibtex
---

@@

# Abstract {-}
